Application-Level Regression Testing Framework using Jenkins

### 2017-06-01 manuscript_ccpe/manuscript.tex
Reformatted for CCPE submission.

\documentclass[10pt, conference, compsocconf]{IEEEtran}

\usepackage{graphicx}
\usepackage{algorithmic,listings}
\lstset{language=C,basicstyle=\small\ttfamily, basewidth=0.51em}
\usepackage{url}
\usepackage{tabularx}
\usepackage{subfig}
\usepackage{float}
\usepackage{underscore}
\usepackage{url}
% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\graphicspath{{figures/}}
\pagestyle{plain}

\newcommand\blfootnote[1]{%
  \begingroup
  \renewcommand\thefootnote{}\footnote{#1}%
  \addtocounter{footnote}{-1}%!TEX encoding = UTF-8 Unicode
  \endgroup
}

@@

\title{Application-Level Regression Testing Framework using Jenkins}

% author names and affiliations 
% use a multiple column layout for up to two different
% affiliations

% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
%

\author{
  \IEEEauthorblockN{Reuben D. Budiardja}
  \IEEEauthorblockA{
    National Center for Computational Sciences\\
    Oak Ridge National Laboratory, Oak Ridge, TN 37831\\
    reubendb@ornl.gov}

\and

  \IEEEauthorblockN{Timothy Bouvet, Galen Arnold}
  \IEEEauthorblockA{
    National Center for Supercomputing Applications\\
    University of Illinois at Urbana-Champaign, 61801\\
    tbouvet@illinois.edu, gwarnold@illinois.edu
  }

}

% make the title area
\maketitle
\thispagestyle{plain}

\begin{abstract}
Monitoring and testing for regression of large scale systems such as the NCSA's Blue Waters supercomputer are challenging tasks. 
In this paper we describe the solution we came up with to perform those tasks. 
Our goal was to find an automated solution for running user-level regression tests to evaluate system usability and performance.
Jenkins, an automation server software, was chosen for its versatility, large user base, and multitude of plugins including collecting data and plotting test results over time. 
We describe our Jenkins deployment to launch and monitor jobs on remote HPC system, perform authentication with one-time password, and integrate with our LDAP server for its authorization. 
We show some use cases and describe our best practices for successfully using Jenkins as a user-level system-wide regression testing and monitoring framework for large supercomputer systems.

\end{abstract}

\begin{IEEEkeywords}
System-monitoring; Regression-testing; Applications; Performance; Benchmarking
\end{IEEEkeywords}

\blfootnote{\textbf{Notice of copyright}: This manuscript has been authored by UT-Battelle, LLC under Contract No. DE-AC05-00OR22725 with the U.S. Department of Energy. The United States Government retains and the publisher, by accepting the article for publication, acknowledges that the United States Government retains a non-exclusive, paid-up, irrevocable, worldwide license to publish or reproduce the published form of this manuscript, or allow others to do so, for United States Government purposes. The Department of Energy will provide public access to these results of federally sponsored research in accordance with the DOE Public Access Plan (http://energy.gov/downloads/doe-public-access-plan).

This paper has been submitted as an article in a special issue of Concurrency and Computation Practice and Experience on the Cray User Group 2017.}

>>>>

\documentclass[AMA]{WileyNJD-v1}

\articletype{CUG2017 Conference Proceeding}

\usepackage{graphicx}
%\usepackage{algorithmic,listings}
\usepackage{listings}
\lstset{language=C,basicstyle=\small\ttfamily, basewidth=0.51em}
\usepackage{url}
\usepackage{tabularx}
\usepackage{subfig}
\usepackage{float}
\usepackage{underscore}
\usepackage{url}

\graphicspath{{figures/}}

\raggedbottom

@@

\title{Application-Level Regression Testing Framework using Jenkins\protect\thanks{\textbf{Notice of copyright}: This manuscript has been authored by UT-Battelle, LLC under Contract No. DE-AC05-00OR22725 with the U.S. Department of Energy. The United States Government retains and the publisher, by accepting the article for publication, acknowledges that the United States Government retains a non-exclusive, paid-up, irrevocable, worldwide license to publish or reproduce the published form of this manuscript, or allow others to do so, for United States Government purposes. The Department of Energy will provide public access to these results of federally sponsored research in accordance with the DOE Public Access Plan (http://energy.gov/downloads/doe-public-access-plan).}}

\author[1]{Reuben D. Budiardja*}

\author[2]{Timothy Bouvet}

\author[2]{Galen Arnold}

\authormark{Budiardja \textsc{et al}}

\address[1]{\orgdiv{National Center for Computational Sciences}, \orgname{Oak Ridge National Laboratory}, \orgaddress{\state{Oak Ridge, TN 37831}, \country{USA}}}

\address[2]{\orgdiv{National Center for Supercomputing Applications}, \orgname{University of Illinois at Urbana-Champaign}, \orgaddress{\state{IL 61801}, \country{USA}}}

\corres{*Reuben D. Budiardja, Oak Ridge National Laboratory, One Bethel Valley Road, P.O. Box 2008, MS-6008, Oak Ridge, TN 37831-6008 \email{reubendb@ornl.gov}}

\abstract[Summary]{Monitoring and testing for regression of large scale systems such as the NCSA's Blue Waters supercomputer are challenging tasks. 
In this paper we describe the solution we came up with to perform those tasks. 
Our goal was to find an automated solution for running user-level regression tests to evaluate system usability and performance.
Jenkins, an automation server software, was chosen for its versatility, large user base, and multitude of plugins including collecting data and plotting test results over time. 
We describe our Jenkins deployment to launch and monitor jobs on remote HPC system, perform authentication with one-time password, and integrate with our LDAP server for its authorization. 
We show some use cases and describe our best practices for successfully using Jenkins as a user-level system-wide regression testing and monitoring framework for large supercomputer systems.}

\keywords{System-monitoring; Regression-testing; Applications; Performance; Benchmarking}

\maketitle
